Fig1

### 2020-04-21 analysis/figure-1.Rmd
new fig 1

# prep for tsne

chartsne <- subsetmaketsne(tissuelevels, charlevels, sexlevels)
hyptsne <- subsetmaketsne("hypothalamus", charlevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", charlevels, sexlevels)
gontsne <- subsetmaketsne("gonads", charlevels, sexlevels)

ftsne <-  subsetmaketsne(tissuelevels, charlevels, "female")
mtsne <-  subsetmaketsne(tissuelevels, charlevels, "male")

```

@@

```{r fig1, fig.width=7.25, fig.height=7.25}

a <- png::readPNG("../figures/images/fig_fig1a.png")
a <- ggdraw() +  draw_image(a, scale = 1)

@@

bcd <- plot_grid(b,c,d, nrow = 1, labels = c("B", "C", "D"), label_size = 8 )
abcd <- plot_grid(a, bcd, nrow = 2, labels = c("A"), label_size = 8, rel_heights = c(1,1))

e <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs( x = NULL)  + 
  facet_wrap(~sex, scales = "free")

g <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(  x = NULL) + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

i <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n")

egi <- plot_grid(e,g,i, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("E", "G", "I"), label_size = 8)

# hyp
f <- makebargraph("hypothalamus","DEGs", 0, 1250) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  
# pit
h <- makebargraph("pituitary","DEGs", 0, 1250)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  
# gon
j <- makebargraph("gonad","DEGs", 0, 1250) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)

@@

efghij <- plot_grid(egi, fhj, nrow = 1, align = "h", rel_widths = c(1.5,2))

fig1 <- plot_grid(abcd, efghij, nrow = 2, rel_heights = c(1,1.5))
fig1
```

>>>>

# prep for tsne
chartsne <- subsetmaketsne(tissuelevels, charlevels, sexlevels)
hyptsne <- subsetmaketsne("hypothalamus", charlevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", charlevels, sexlevels)
gontsne <- subsetmaketsne("gonads", charlevels, sexlevels)

ftsne <-  subsetmaketsne(tissuelevels, charlevels, "female")
mtsne <-  subsetmaketsne(tissuelevels, charlevels, "male")
```

@@

```{r fig1, fig.width=7.25, fig.height=7.25}
a <- png::readPNG("../figures/images/fig_fig1b.png")
a <- ggdraw() +  draw_image(a, scale = 1)

@@

abcd <- plot_grid(a,b,c,d, nrow = 1, labels = c("A", "B", "C", "D"), label_size = 8 )

e <- png::readPNG("../figures/images/fig_fig1a.png")
e <- ggdraw() +  draw_image(e, scale = 1)

f <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(x = NULL, subtitle = "hypothalamus")  + 
  facet_wrap(~sex, scales = "free")

h <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(x = NULL, subtitle = "pituitary") + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n", subtitle = "gonads")

@@

# hyp
g <- makebargraph("hypothalamus","DEGs", 0, 4300) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  +
  labs(subtitle = "hypothalamus")
# pit
i <- makebargraph("pituitary","DEGs", 0, 4300)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = "pituitary")
# gon
k <- makebargraph("gonad","DEGs", 0, 4300) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = "gonads")

gik <- plot_grid(g,i,k, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("G", "I", "K"), label_size = 8)

fhjgik <- plot_grid(fhj, gik, nrow = 1, align = "h", rel_widths = c(1.5,2))

fig1 <- plot_grid(abcd, e, fhjgik, nrow = 3, rel_heights = c(0.7,0.5,1.5),
                  labels = c(" ","E"), label_size = 8 )
fig1
```
